데이터 과학을 위한 저작도구: Computational Documents

### 2020-04-14 automation-kasdba.Rmd
added published paper andd links

- [블로그: ~~로봇~~ 자동화가 빼앗는 일자리 그리고 나](https://statkclee.github.io/ds-authoring/ds-bundang-2019.html)
- [한국디지털경영학회 투고 논문 ](https://github.com/statkclee/comp_document/blob/gh-pages/tutorial/paper/paper.pdf)

>>>>

- [블로그: ~~로봇~~ 자동화가 빼앗는 일자리 그리고 나](https://statkclee.github.io/ds-authoring/ds-bundang-2019.html)
- [한국디지털경영학회 투고 논문 ](https://github.com/statkclee/comp_document/blob/gh-pages/tutorial/paper/paper.pdf)
- [한국디지털경영학회 게재 논문](http://journal.kasdba.or.kr/journal/article.php?code=70468&vol=6&no=2&start_page=39&end_page=50): [**다운로드**](data/00006_002_39.pdf)
    - Lee Kwang-Chun,Yong-Woo Joo (2020), "Competitive Factors and Collaboration Methods for Jobs between People and AI", Digital Management Review Vol.6 No.2 pp.39-50
    - 이광춘, 주용우 (2020), "사람과 인공지능의 일자리 경쟁 요인과 협업 방안" 디지털경영연구 Vol.6 No.2 pp.39-50
